---
title: "R Presentation <br>reveal-js<p style='text-transform: none;'><small>February 24th, 2021</small></p>"
bibliography: bibliography.bib
csl: institute-of-mathematical-statistics.csl
output:
  revealjs::revealjs_presentation:
    theme: sky
    highlight: pygments
    center: true
    increment: true
    self_contained: false  # important to keep plotly.html as an external file and not embedded 
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

# Example of slides

## Slide with Bullets {data-transition="zoom" data-background=#ff0000 incremental=true}

- This is the first to be shown [@R4DS; @ggplot2].

- This is the second to be shown

> - This is not incremental
> - Neither this one

## Slide with Bullets {data-transition="zoom" data-background=#00ff00}
<ul>
<li class="fragment fade-out" data-fragment-index="1">fade-out 1</li>
<li class="fragment fade-out" data-fragment-index="3">fade-out 3</li>
<li class="fragment fade-out" data-fragment-index="2">fade-out 2</li>
</ul>

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

Here the code that produces the plot is hidden

```{r, echo=FALSE, out.height = "350px"}
plot(cars)
```

# Transitions

## Test of different type of transitions
```{js echo=FALSE}
var my_data="Reveal JS";
``` 
<p class="fragment grow fade-in" data-fragment-index="1">grow</p>

<p class="fragment shrink" data-fragment-index="3">shrink</p>

<p class="fragment fade-out" data-fragment-index="2">fade-out</p>

<p class="fragment fade-up" data-fragment-index="4">fade-up (also down, left and right!)</p>

<p>
<span style="display: inline-block;" class="fragment fade-right" data-fragment-index="5">fade-right, </span>
<span style="display: inline-block;" class="fragment fade-up" data-fragment-index="6">up, </span>
<span style="display: inline-block;" class="fragment fade-down" data-fragment-index="7">down, </span>
<span style="display: inline-block;" class="fragment fade-left" data-fragment-index="8">left</span>
</p>
						
<p class="fragment fade-up" data-fragment-index="9">fades in, then out when we move to the next step</p>

<p class="fragment" data-fragment-index="10">again fade-in</p>

# Slides with dynamic plots

## Plotly graph
```{r, include=FALSE}
library(plotly)
```
```{r echo=FALSE}

trace_0 <- rnorm(100, mean = 5)
trace_1 <- rnorm(100, mean = 0)
trace_2 <- rnorm(100, mean = -5)
x <- c(1:100)

data <- data.frame(x, trace_0, trace_1, trace_2)

p <- plot_ly(data, x = ~x, y = ~trace_0, name = 'trace 0', type = 'scatter', mode = 'lines') %>%
  add_trace(y = ~trace_1, name = 'trace 1', mode = 'lines+markers') %>%
  add_trace(y = ~trace_2, name = 'trace 2', mode = 'markers')

htmlwidgets::saveWidget(p,'plotly.html')
knitr::include_url("plotly.html", height = "576px")
```

## r2d3 graph
```{r setup, echo=FALSE}
library(r2d3)
bars <- c(10, 20, 30, 15, 19, 44, 2)
```

```{d3 data=bars, options=list(color = 'orange'), out.width = "400px", out.height = "200px"}
svg.selectAll('rect')
  .data(data)
  .enter()
    .append('rect')
      .attr('width', d => d * 10)
      .attr('height', '20px')
      .attr('y', (d, i) => i * 22)
      .attr('fill', options.color);
```

## r2d3 graph with external file
```{r, out.width = "400px", out.height = "200px"}
library(r2d3)
r2d3(data=c(0.3, 0.6, 0.8, 0.95, 0.40, 0.20), script = "d3-barchart.js")
```

## Inserting our pie-chart
<div class="p_iframe">
<iframe frameborder="0" seamless='seamless' scrolling=no src="d3-piechart.html"></iframe>
</div>

# Few more things

## Embedding javascript
```html
<div id="testjs">Hello</div>
```  
<div id="testjs">Hello</div>
```{js}
function change_color(){
  var div=document.getElementById('testjs')
  div.style.color='green';
  div.style.fontSize = "150%";
  div.innerHTML = "Hello " + my_data;
}
```  
```html
<button onclick="change_color">Change color</button>
```  
```{css echo=FALSE}
.btn {
  display: inline-block;
  -webkit-box-sizing: content-box;
  -moz-box-sizing: content-box;
  box-sizing: content-box;
  cursor: pointer;
  padding: 10px 20px;
  border: 1px solid #018dc4;
  -webkit-border-radius: 3px;
  border-radius: 3px;
  font: normal 16px/normal "Times New Roman", Times, serif;
  color: rgba(255,255,255,0.9);
  -o-text-overflow: clip;
  text-overflow: clip;
  background: #0199d9;
  -webkit-box-shadow: 2px 2px 2px 0 rgba(0,0,0,0.2) ;
  box-shadow: 2px 2px 2px 0 rgba(0,0,0,0.2) ;
  text-shadow: -1px -1px 0 rgba(15,73,168,0.66) ;
  -webkit-transition: all 300ms cubic-bezier(0.42, 0, 0.58, 1);
  -moz-transition: all 300ms cubic-bezier(0.42, 0, 0.58, 1);
  -o-transition: all 300ms cubic-bezier(0.42, 0, 0.58, 1);
  transition: all 300ms cubic-bezier(0.42, 0, 0.58, 1);
}
```  
<button type="button" class="btn" onclick="change_color()">Change color and font size</button>

## Embedding CSS
Some embedded CSS code
```{css}
#testcss {
  color: red;
}
```

```html
<div id="testcss">Hello</div>
```
<div id="testcss">Hello</div>

# Equations

## getting started

We can write fractions: $\frac{2}{3}$. We can also handle things like estimated population growth rate, e.g., $\hat{\lambda}=1.02$. And, $\sqrt{4}=2$.

$$\alpha, \beta,  \gamma, \Gamma$$

$$a \pm b$$
$$x \ge 15$$
$$a_i \ge 0~~~\forall i$$

## Matrix

$$A_{m,n} =
 \begin{pmatrix}
  a_{1,1} & a_{1,2} & \cdots & a_{1,n} \\
  a_{2,1} & a_{2,2} & \cdots & a_{2,n} \\
  \vdots  & \vdots  & \ddots & \vdots  \\
  a_{m,1} & a_{m,2} & \cdots & a_{m,n}
 \end{pmatrix}$$
 
## Referencing equations

```latex
\begin{equation}
  \int_0^\infty \frac{x^3}{e^x-1}\,dx = \frac{\pi^4}{15}
  \label{eq:sample}\tag{1}
\end{equation} 
```

\begin{equation}
  \int_0^\infty \frac{x^3}{e^x-1}\,dx = \frac{\pi^4}{15}
  \label{eq:sample}\tag{1}
\end{equation}

Refer to it using ```$\eqref{eq:sample}$```, e.g., see $\eqref{eq:sample}$

# References

##
